
\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% Minimal formatting for ATS
\pagestyle{empty}
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{ABHISHEK TIWARI}} \\ \vspace{2mm}
    \href{mailto:abhishektiwari6827@gmail.com}{abhishektiwari6827@gmail.com} | +91 6283995304 | Chandigrah, India \\
    \href{https://www.linkedin.com/in/abhishek-tiwariiii}{LinkedIn: abhishek-tiwariiii} | \href{https://github.com/Abhishek6827}{GitHub: Abhishek6827} | \href{https://abhishek6827.github.io/Portfolio/}{Portfolio}
\end{center}

% Education
\section{Education}
\textbf{Bachelor of Technology in Computer Science} \hfill 2022 -- 2026 \\
Chandigarh Group of Colleges, Jhanjeri \hfill CGPA: 7.7/10 \\
\vspace{2mm}
\textbf{Senior Secondary (XII)} \hfill 2022 \\
Adarsh Senior Secondary School \hfill Percentage: 87.6\%

% Experience
\section{Experience}

\textbf{Full Stack Developer} \hfill Nov 2025 -- Jan 2026 \\
Indian Capital and Investment (Coimbatore) Limited \hfill Remote
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Developed secure payment gateway integrations using Stripe and Zoho Payments, enabling seamless transaction processing.
    \item Built scalable backend services with Next.js and Firebase, implementing real-time data synchronization.
    \item Designed and deployed webhooks for automated transaction status updates and notifications via Resend API.
    \item Integrated Notion API to automate internal record-keeping, streamlining administrative workflows.
    \item utilised Warp and Ngrok for secure local tunnel testing and development workflows.
\end{itemize}

\textbf{Software Developer} \hfill Aug 2024 -- Oct 2025 \\
Vasnaani Education \hfill Remote
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Developed and maintained the official Vasnaani Education website, optimizing for performance and scalability.
    \item Collaborated with cross-functional teams to design user-centric, responsive web interfaces.
    \item Integrated Django REST APIs with React frontend modules to ensure seamless data flow.
    \item Optimized database structures and resolved critical UI/UX bugs, improving user retention.
\end{itemize}

\textbf{Full-Stack Developer Intern} \hfill Jan 2024 -- June 2024 \\
Hoping Minds \hfill Mohali, India
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Developed web applications using React, Redux, and Django, ensuring robust functionality.
    \item Implemented responsive designs and optimized application performance for diverse devices.
    \item Participated in code reviews and adhered to best practices for clean, maintainable code.
\end{itemize}

\textbf{Web Developer} \hfill Nov 2023 -- Dec 2023 \\
Quizario \hfill Remote
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Built interactive quiz applications utilizing modern web technologies.
    \item Implemented user authentication and secure data management features.
    \item Optimized application performance and enhanced overall user experience.
\end{itemize}

% Projects
\section{Projects}

\textbf{TempusMail} | \textit{Next.js, Firebase, Notion API, Tailwind CSS} \hfill \href{https://tempusmail-backend--tempusmail6827.us-central1.hosted.app/}{Live Demo}
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Engineered a temporary email service with real-time email reception and a modern, responsive UI.
    \item Integrated Notion Database for efficient backend storage and management.
\end{itemize}

\textbf{Myntra Clone} | \textit{React, Redux, CSS} \hfill \href{https://abhishek6827.github.io/Myntra/}{Live Demo}
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Developed a functional fashion e-commerce platform clone with a modern user interface.
    \item Implemented state management using Redux for seamless cart and product handling.
\end{itemize}

\textbf{Skill\_Up} | \textit{React, Firebase} \hfill \href{https://abhishek6827.github.io/Skill_Up/}{Live Demo}
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item Created a comprehensive learning platform for browsing and accessing online courses.
    \item Utilized Firebase for secure user authentication and real-time database management.
\end{itemize}

% Skills
\section{Technical Skills}
\textbf{Languages:} C/C++, JavaScript (ES6+), Python, SQL, HTML5, CSS3, TypeScript \\
\textbf{Frontend:} React.js, Redux, Next.js, Tailwind CSS, Bootstrap, Material UI, Framer Motion \\
\textbf{Backend:} Node.js, Express.js, Django, Firebase \\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL \\
\textbf{Tools \& APIs:} Git, GitHub, VS Code, Postman, Stripe, Zoho Payments, Resend API, Notion API, Warp, Ngrok

% Certifications
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={-}]
    \item \textbf{Data Structure and Algorithm in C++} -- Coding Ninjas (2023)
    \item \textbf{Scientific Computing with Python} -- FreeCodeCamp (2023)
    \item \textbf{Postman API Fundamentals Student Expert} -- Postman (2024)
\end{itemize}

\end{document}
